Stay in shape! Homework exam II

### 2016-03-30 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
trying to prove the lemma

\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
%TODO: een beeetje overtypen van 4.5
Let $1 \leq i \leq n$, let $C_i$ be the defined as above and let $d_i$ be
the largest disk in $C_i$. Then we have
\begin{enumerate}[i]
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
\end{enumerate}

>>>>

\begin{enumerate}[(i)]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
\paragraph{Lemma}
Let $1 \leq i \leq n$, let $C_i$ be the defined as above and let $d_i$ be
the largest disk in $C_i$. Then we have
\begin{enumerate}[(i)]
	\item If $d_{i-1} \in h_i,$ $then$ $d_i = d_{i-1}$
%TODO: C = nill? dat klopt volgens mij niet
	\item If $d_{i-1} \not\in h_{i},$ $then$ $C_i = \emptyset$
		or $b_i \in l_i$ where $b_i$ is the boundary of $d_i$ and $l_i$
		is the line bounding $h_i$.
\end{enumerate}
\paragraph{Proof}
\begin{enumerate}[(i)]
	\item Let $d_{i-1} \in h_i$. Because $C_i = C_{i-1}\cap h_i$ and
		$d_{i-1} \in C_{i-1}$. Furtheremore,the optimal disk in $C_i$
		cannot be better than the optimal disk in $C_{i-1}$, since
		$C_i \subseteq C_{i-1}$. Hence, $d_{i-1}$ is the optimal disk
		in $C_i$ as well.
	\item Let $d_{i-1} \not\in h_{i}$. Suppose for a contradiction that
		$C_i \not\emptyset$ and that $b_i \not\in l_i$. Now consider
		the line segment $\overline{cx_{i-1}cx_i}$ where $cx_i$ is the
		center on the x-axis of disk $d_i$. We have
		$d_{i-1} \in C_{i-1}$ and, since $C_i \subset C_{i-1}$, also
		$d_i \in C_{i-1}$. 
\end{enumerate}
